Malacology: A Programmable Storage System

### 2017-03-16 paper/1_intro.tex
paper: fix line breaks
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: camera ready
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

A storage system implements abstractions designed to persistently store data
and must exhibit a high level of correctness to prevent data loss.  Storage
systems have evolved around storage devices that often were orders of magnitude
slower than CPU and memory, and therefore could dominate overall performance if
not used carefully. Over the last few decades members of the storage systems
community have developed clever strategies to meet correctness requirements
while somewhat hiding the latency of traditional storage
media~\cite{brewer_disks_2016}. To avoid lock-in by a particular vendor, users
of storage systems have preferred systems with highly standardized APIs and
lowest common denominator abstract data types such as blocks of bytes and byte
stream files~\cite{armbrust_view_2010}.

@@

\item A high-performance distributed shared log service called ZLog, that is an
implementation of CORFU.~\cite{balakrishnan_corfu_2012}

>>>>

A{\let\thefootnote\relax\footnote{$^{\dag}$ These authors contributed equally to
this work.}} storage system implements abstractions designed to persistently
store data and must exhibit a high level of correctness to prevent data loss.
Storage systems have evolved around storage devices that often were orders of
magnitude slower than CPU and memory, and therefore could dominate overall
performance if not used carefully. Over the last few decades members of the
storage systems community have developed clever strategies to meet correctness
requirements while somewhat hiding the latency of traditional storage
media~\cite{brewer_disks_2016}. To avoid lock-in by a particular vendor, users
of storage systems have preferred systems with highly standardized APIs and
lowest common denominator abstract data types such as blocks of bytes and byte
stream files~\cite{armbrust_view_2010}.

@@

\item A high-performance distributed shared log service called ZLog, that is an
implementation of CORFU~\cite{balakrishnan_corfu_2012}

### 2017-03-16 paper/paper.tex
paper: camera ready
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\usepackage{amsmath}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{pifont}
\usepackage{color}
\usepackage{comment}

@@

\authorinfo{Michael A. Sevilla, Noah Watkins, Ivo Jimenez, \\Peter Alvaro, Shel Finkelstein, Jeff LeFevre, Carlos Maltzahn}
           {University of California, Santa Cruz}
           {\{msevilla, jayhawk, ivo\}@soe.ucsc.edu, \{palvaro, shel\}@ucsc.edu, \{jlefevre, carlosm\}@soe.ucsc.edu}

>>>>

\usepackage{amsmath}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{pifont}
\usepackage{color}
\usepackage{comment}
\usepackage{marvosym}

@@

\authorinfo{Michael A. Sevilla$^{\dag}$, Noah Watkins$^{\dag}$, Ivo Jimenez, \\Peter Alvaro, Shel Finkelstein, Jeff LeFevre, Carlos Maltzahn}
           {University of California, Santa Cruz}
           {\{msevilla, jayhawk, ivo\}@soe.ucsc.edu, \{palvaro, shel\}@ucsc.edu, \{jlefevre, carlosm\}@soe.ucsc.edu}
